Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Validated Saturn-Sized Planet in IC~2602

### 2020-07-13 paper/ms.tex
update manuscript

We observed three transits with the 0.40m ASTEP telescope at the
Concordia base on the Antarctic Plateau \citep{daban_astep_2010}.
Concordia base is operated jointly by the French and Italian polar
institutes, IPEV and PNRA.  Its position on the Antarctic Plateau at
lat $75.06^\circ$S, long $123.3^\circ$E allows it to take advantage of
the continuous night during Austral winter.  The weather is of
photometric quality for about two-thirds of each winter
\citep{crouzet_four_2018}.

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.46\textwidth]{f3.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Follow-up speckle-imaging and velocimetry of \tn.} {\it Top:}
    SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments. Star A ($\Delta T=4.7$, $2.3''$
    west) is detected in the autocorrelation function, and is also a
    resolved Gaia source.  It is co-moving with \tn, and its parallax
    and on-sky position imply that it is physically separated from
    \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:} Radial velocity
    (RV) measurements, with best-fit instrument offsets and jitter
    terms included.  The expected scatter from starspots based on
    $v\sin i$ and the photometric modulation amplitude is of order
    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
    orbital ephemeris of \pn.  The planet is not detected.  The black
    line shows a circular Keplerian orbit representing the $3\sigma$
    upper mass limit.
		\label{fig:followup}
	}
\end{figure}

@@

\subsubsection{FEROS}
We acquired 13 spectra using the FEROS echelle spectrograph, mounted
on the MPG 2.2m telescope at the European Soutern Observatory in La
Sille, Chile \citep{kaufer_commissioning_1999}.  FEROS has a
resolution of $\approx 48{,}000$ across a spectra range of
350--920$\,$nm. It has a remarkably high efficiency of $\approx 20\%$.

We used the dedicated instrument pipeline to extract 1-dimensional,
wavelength calibrated spectra.  To measure radial velocities, \edit1{
Rafael/Paula TODO: what procedure was used?  What software packages?}.  The
velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:followup}.

\subsubsection{Veloce}
We acquired 34 spectra over 10 visits of \tn\ using the Veloce
spectrograph, mounted on the AAT 4.0m telescope at Siding Spring
Observatory near Coonabarabran, Australia \citep{gilbert_veloce_2018}.
In the ``Rosso'' instrument-mode, Veloce provides coverage from
600--950$\,$nm at a spectral resolution of $\approx 80{,}000$.

Many of the exposures were taken in average or poor seeing conditions,
when fiber-to-fiber cross-contamination on the IFU-style fiber feed is
strongest.  To reduce the spectra to velocities, we cross-correlated
against a high S/N template of $\delta$ Pavonis.  The velocity RMS
seen across each visit was hundreds of meters per second, likely due to
uncorrected fiber-to-fiber cross-contamination.  For
analysis purposes, we averaged across each visit, and set the velocity
uncertainties to be the standard deviation of the per-visit exposures.
The velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:followup}.

@@

The posteriors from fitting the TESS data alone are given in
Table~\ref{tab:posterior}.  Both approaches show that the transit is
nearly grazing.   The relevant posterior probabilities are shown in
Figure~\ref{fig:subsetcorner}.  To be precise, some of the posterior
has $b < 1 - R_{\rm p}/R_\star$ and therefore formally is not grazing,
and some of the posterior formally is grazing. For short-hand
convenience, we refer to this as grazing.  From experimenting with the
fits, we found that in the absence of a strong prior on the stellar
density, the inherent degeneracy between the impact parameter and
planet-to-star size ratio would have been much stronger.  However, our
priors on the stellar parameters from the cluster isochrone fit are
strong enough that we can derive two-sided limits on the
planet-to-star size ratio.

% TODO: decide whether to include this. it's not necessary!
% \subsubsection{Additional Transits}
% None of the extra dips in the PDCSAP light-curve (e.g., ``up-down''
% spikes at BTJD 1572 and 1601) seem likely to be planetary
% We checked that i) they were not present in the SAPFLUX light-curves,
% and ii) that they were not present in the CDIPS light-curves (either
% raw, or PCA-detrended).
% To make this quantitative, we did injection-recovery(?)

@@

\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
	\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019}
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:agol19}
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol19, exoplanet:kipping13, exoplanet:luger18,
  	exoplanet:theano}.
	\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
  \texttt{IPython} \citep{perez_2007},
	\texttt{isochrones} \citep{morton_2015_isochrones},
	\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  \texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
	\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
  \texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}

>>>>

We observed three transits with the 0.40m ASTEP telescope at the
Concordia base on the Antarctic Plateau \citep{daban_astep_2010}.
Concordia base is operated jointly by the French and Italian polar
institutes, IPEV and PNRA.  Its position on the Antarctic Plateau
allows it to take advantage of
the continuous night during Austral winter.  The weather is of
photometric quality for about two-thirds of each winter
\citep{crouzet_four_2018}.

@@

		\vspace{-0.3cm}
		\subfloat{
			\includegraphics[width=0.47\textwidth]{f3.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Speckle-imaging and velocimetry of \tn.} {\it Top:}
    SOAR HRCam contrast limits derived from point-source
    injection-recovery experiments. Star A ($\Delta T=4.7$, $2.3''$
    west) is detected, and is also a
    resolved Gaia source.  It is co-moving with \tn, and its parallax
    and on-sky position imply that it is physically separated from
    \tn\ by $6.6\pm 0.1\,{\rm pc}$.  {\it Middle:} Radial velocity
    (RV) measurements, with best-fit instrument offsets and jitter
    terms included.  The expected scatter from starspots based on
    $v\sin i$ and the photometric modulation amplitude is of order
    300m$\,$s$^{-1}$.  {\it Bottom:} RV measurements phased to the
    orbital ephemeris of \pn.  The planet is not detected.  The black
    line shows a circular Keplerian orbit representing the $3\sigma$
    upper mass limit.
		\label{fig:followup}
	}
\end{figure}

@@

\subsubsection{FEROS}
TOI 837.01 was monitored with the FEROS echelle spectrograph
\citep{kaufer_commissioning_1999}, mounted on the MPG 2.2m telescope
at the ESO La Sille Observatory, in Chile. FEROS has a resolution of
$\approx$48,000 across a spectral range of 350–920 nm. It has a
remarkably high efficiency of $\approx$20\%. We obtained 13 spectra of
\tn\ between July 5 of 2019 and March 14 of 2020 in the context of the
Warm gIaNts with tEss (WINE) collaboration, which focuses on the
systematic characterization of TESS transiting giant planets with
moderately long orbital periods \citep[{\it
e.g.},][]{brahm:2019,jordan:2020}.  We adopted exposure times of 500
and 600 seconds and the observations were performed with the
simultaneous calibration mode for tracing the instrumental velocity
variations with a comparison fiber illuminated with a ThAr lamp. FEROS
data was processed with the \texttt{ceres} pipeline
\citep{brahm_2017_ceres}, which delivers precision radial velocities
and bisector span measurements through cross-correlation of the
extracted spectra with a binary mask resembling the properties of a
G2V star. The radial velocities are given in Table~\ref{tab:rvs},
and shown in Figure~\ref{fig:followup}.

\subsubsection{Veloce}
We acquired 34 spectra over 10 visits of \tn\ using the Veloce
spectrograph, mounted on the AAT 4.0m telescope at Siding Spring
Observatory near Coonabarabran, Australia \citep{gilbert_veloce_2018}.
In the ``Rosso'' instrument-mode, Veloce provides coverage from
600--950$\,$nm at a spectral resolution of $\approx 80{,}000$.  Many
of the exposures were taken in average or poor seeing conditions, when
fiber-to-fiber cross-contamination on the IFU-style fiber feed is
strongest.  To reduce the spectra to velocities, we cross-correlated
against a high S/N template of $\delta$ Pavonis.  The velocity RMS
seen across each visit was hundreds of meters per second, likely due
to uncorrected fiber-to-fiber cross-contamination.  For analysis
purposes, we averaged across each visit, and set the velocity
uncertainties to be the standard deviation of the per-visit exposures.
The velocities are given in Table~\ref{tab:rvs}, and shown in
Figure~\ref{fig:followup}.

@@

The posteriors from fitting the TESS data alone are given in
Table~\ref{tab:posterior}.  The condition for a grazing transit is
whether the impact parameter is below $1 - R_{\rm p}/R_\star$.  The
transit is therefore either grazing, or nearly grazing.   The relevant
posterior probabilities are shown in Figure~\ref{fig:subsetcorner}.
From experimenting with the priors, we found that in the absence of a
strong prior on the stellar density, the inherent degeneracy between
the impact parameter and planet-to-star size ratio would have been
much stronger.  In the absence of precise information about the star,
a larger fraction of the posterior would therefore have been grazing.
However, our priors on the stellar parameters from the cluster
isochrone fit break this degeneracy, enabling us to report two-sided
limits on the planet-to-star size ratio.

@@

\software{
  \texttt{astrobase} \citep{bhatti_astrobase_2018},
  %\texttt{astroplan} \citep{astroplan2018},
	\texttt{AstroImageJ} \citep{collins_astroimagej_2017},
  \texttt{astropy} \citep{astropy_2018},
  \texttt{astroquery} \citep{astroquery_2018},
  %\texttt{BATMAN} \citep{kreidberg_batman_2015},
  \texttt{ceres} \citep{brahm_2017_ceres},
  \texttt{cdips-pipeline} \citep{bhatti_cdips-pipeline_2019},
  \texttt{corner} \citep{corner_2016},
  %\texttt{emcee} \citep{foreman-mackey_emcee_2013},
  \texttt{exoplanet} \citep{exoplanet:agol19}
  \texttt{exoplanet} \citep{exoplanet:exoplanet}, and its
  dependencies \citep{exoplanet:agol19, exoplanet:kipping13, exoplanet:luger18,
  	exoplanet:theano},
	\texttt{IDL Astronomy User's Library} \citep{landsman_1995},
  \texttt{IPython} \citep{perez_2007},
	\texttt{isochrones} \citep{morton_2015_isochrones},
	\texttt{lightkurve} \citep{lightkurve_2018},
  \texttt{matplotlib} \citep{hunter_matplotlib_2007}, 
  \texttt{MESA} \citep{paxton_modules_2011,paxton_modules_2013,paxton_modules_2015}
  \texttt{numpy} \citep{walt_numpy_2011}, 
  \texttt{pandas} \citep{mckinney-proc-scipy-2010},
  \texttt{pyGAM} \citep{serven_pygam_2018_1476122},
  \texttt{PyMC3} \citep{salvatier_2016_PyMC3},
  \texttt{radvel} \citep{fulton_radvel_2018},
  %\texttt{scikit-learn} \citep{scikit-learn},
  \texttt{scipy} \citep{jones_scipy_2001},
  \texttt{tesscut} \citep{brasseur_astrocut_2019},
	\texttt{VESPA} \citep{morton_efficient_2012,vespa_2015},
  \texttt{webplotdigitzer} \citep{rohatgi_2019},
  \texttt{wotan} \citep{hippke_wotan_2019}.
}
